---
title: "biodiverse_path_reference"
author: "Nunzio Knerr"
date: "Monday, September 01, 2014"
output: html_document
runtime: shiny
---
```{r, echo=FALSE}
#require(shiny)

datas <- data.frame(directory = c("a", "a", "a", "b", "b", "c"), file = sprintf("file%d", 1:6))

list(
  ui = basicPage(
    sidebarPanel(
      selectInput("directory", "Select a directory", choices = levels(datas$directory), selected = levels(datas$directory)[1]),
      tags$hr(),
      selectInput("files", "Select files", choices = datas$file[datas$directory == levels(datas$directory)[1]], multiple = TRUE)
    )
  ),
  server = function(input, output, session) {

    observe({
      directory <- input$directory

      updateSelectInput(session, "files", choices = datas$file[datas$directory == directory])
    })
  }
)
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



