---
title: "Check & Install Packages"
runtime: shiny
output: html_document
---

This script checks and installs a number of packages if they are not already installed on the system to use it just select all of the text and run it in R. It basically speeds up the process of getting an R install up and running so you don't need to manually install packages.

## Inputs and Outputs

click the install packages button below to install the following packages
```{r, echo=TRUE}
stdpkgs <- c("sp", "maptools", "XML", "RSAGA", "rgdal", "rgeos", "raster", "plyr", "dplyr", "tidyr", "ggplot2", "RColorBrewer", "colorspace", "colorRamps", "spacetime", "aqp", "spatstat", "scales", "stringr", "gWidgets", "phytools", "ape", "apTreeshape") 
otherpkgs <- c("plotKML") 
```

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2),
  
  # Copy the line below to make an action button
  actionButton("action", label = "Check and Install Packages") 
   
  
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})

renderPrint({
    #setInternet2() # this sets an alternative internet. good for proxy if stupid intenet blocking is done
  local({r <- getOption("repos")
         r["CRAN"] <- "http://cran.csiro.au/"
         options(repos=r)
  })
   
  allpkgs <- union(stdpkgs, otherpkgs)
  
  pkgTest <- function(x)
  {
    if (!require(x,character.only = TRUE))
    {
      install.packages(x,dep=TRUE)
      if(!require(x,character.only = TRUE)) stop("Package not found")
    }
  }
    
lapply(allpkgs, pkgTest)
  
})   
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



